Experiments on ANTS Algorithms Without Communication

### 2014-12-09 paper/draft.tex
added more stuff to intro. intro should be done

We study the \emph{Ants Nearby Treasure Search} (ANTS) problem for modelling collective foraging in animal groups. $k$ identical probabilistic agents search for treasure located by an adversary $D$ units away from a central location.

\subsection{Related Works}

\section{The Problem Statement}

@@

\section{Algorithms}

@@

\subsection{Spiral Algorithms}

@@

\subsection{Lines Algorithm}

@@

\section{Experiments and Results}

@@

\section{Conclusion}

>>>>

We study the \emph{Ants Nearby Treasure Search} (ANTS) problem for modelling collective foraging in animal groups. $k$ identical probabilistic agents search for treasure located by an adversary $D$ units away from a central location. The problem is a generalization of a previously studied problem, the \emph{cow-path} problem, which is the case where $k = 1$.

Our project is a combination of a reading project and an experimental project. For the reading project component, we survey three known algorithms for the ANTS algorithm by Feinerman et al. and Lenzen et al. For the experimental project, we show the results of tests run on these algorithms to determine the constants in their runtimes.

The paper is organized as follows. In Section~\ref{problem statement}, we formally state and motivate the problem. We also give a simple argument for why any algorithm solving the problem takes $\Omega(D+D^2/k)$ time. We then outline different algorithm types, and give high-level overviews of the spiral, harmonic, and lines algorithms. In Section~\ref{spiral}, we give a more in-depth explanation of the details of the spiral algorithm of Feinerman et al. We do this for the harmonic algorithm in Section~\ref{harmonic}, and for the lines algorithm in Section~\ref{lines}. In Section~\ref{experiments}, we shift our focus to the experimental part of our project. In that section, we describe our hypotheses, our experimental setup, the results, and our interpretation of the results. We give concluding remarks in Section~\ref{conclusion}.

\section{Problem Setup and Basics}
\label{problem statment}

@@

@@

\section{Spiral Algorithms}
\label{spiral}

@@

\section{Harmonic Algorithm}
\label{harmonic}

\section{Lines Algorithm}
\label{lines}

@@

\section{Experiments and Results}
\label{experiments}

@@

\section{Conclusion}
\label{conclusion}
